{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-30 bmvc_review.tex
Figures 3 and 4 Updated

\begin{figure}[!h]
\centering
\includegraphics[width=0.45\textwidth]{figures/Filters_Details.pdf}
\caption{Examples of three filters; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response. Instead of using a single, correlation
  filter for estimating change of a target's scale and translation, it
  would be better to use more than one correlation filter for better
  estimating change of scale and translation individually.}
\label{fig:Filters}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.5\textwidth]{figures/LearnedFilterComparison.pdf}
\caption{This figure shows that there is marginal difference among the
  scale filters learned either at every frame or at every 5
  frames. The sub-figures at the top row show the scale filters
  trained from every frame and those at the bottom row show the scale
  filters estimated every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure}

>>>>

\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{figures/Filters_Details.pdf}
\caption{Examples of three filters; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=1\textwidth]{figures/LearnedFiltersComparison2.pdf}
\caption{This figure shows that there is marginal difference among the
  scale filters learned either at every frame or at every 5
  frames. The sub-figures at the the left show the scale filters
  trained at every frame and those at the right show the scale
  filters trained at every 5 frames.}
\label{fig:Filters_Comparison}
\end{figure}
